---
title       : Project in Data Products class as part of the DataScience specialization at coursera.org
subtitle    : MPG estimation Shiny app
author      : Andrei Kuebar
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Shiny app created for this project 
URL:https://ierdna.shinyapps.io/project/

This app allowes the user to estimate the Mileage per Gallon of gas of a car based on three parametes:
 - horse power
 - 1/4 mile time
 - transmission type

--- .class #id 
## Model
To estimate the MPG value a multivariable linear regression model was created

R dataset 'mtcars' was used as the data source
```{r}
data(mtcars)
dim(mtcars)
```

--- .class #id
## Model fit

Linear model was fitted as follows:
```{r}
fit <- lm( mpg ~ hp + qsec + am , mtcars)
summary(fit)$coefficient
```

--- .class #id
## Shiny app and source
 - MPG Shiny app is found here: https://ierdna.shinyapps.io/project/
 - GitHub source for the app: https://github.com/andreikubar/dataproducts/tree/master/project




